Changes in accessibility to emergency and community food services during COVID-19 and implications for low income populations in Hamilton, Ontario

### 2021-08-29 Accessibility-Foodbanks-Hamilton/Accessibility-Foodbanks-Hamilton.Rmd
Recreated data package with new foodbank_table.Rmd and ttm_transit.Rmd; knitted README.Rmd after submission to SSM

```{r invoke-data, include=FALSE}
data(data_da_2016)
data(dwelling_network_points_2016)
data(foodbank_locations)
#data(foodbank_table)
data(hamilton_boundary)
data(modes_less40k)
data(population_age_income)
data(ttm_car)
#data(ttm_transit)
data(ttm_walk)

# load updated files manually
load("./output-data-files/ttm_transit.RData")
load("./output-data-files/foodbank_table.RData")
```

>>>>

```{r invoke-data, include=FALSE}
data(data_da_2016)
data(dwelling_network_points_2016)
data(foodbank_locations)
data(foodbank_table)
data(hamilton_boundary)
data(modes_less40k)
data(population_age_income)
data(ttm_car)
data(ttm_transit)
data(ttm_walk)

# load updated files manually
#load("./output-data-files/ttm_transit.RData")
#load("./output-data-files/foodbank_table.RData")
```
